%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {Product Development Engineer - II} % Job title
  {Phenom People} % Organization
  {Hyderabad, Telangana} % Location
  {Jun. 2019 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Working on building a Integration Platform for the talent vertical to integrate Phenom suite with external applicant tracking systems. We considerably reduced the configuration complexity for implementation engineers. And also reduced configuration time by around 60\%.}
      \item {Designed and implemented a RESTful app to help the support team to speed up the client discovery process.}
      \item {Implemented a conditional JSON field mapper UI using drag-end-drop approach. The app was used to map fields from external APIs to Phenom standard fields.}
      \item {Built a standard React template and implemented several custom user interfaces for Apache NiFi processors.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Development Engineer} % Job title
  {Pramati Technologies} % Organization
  {Hyderabad, Telangana} % Location
  {Dec. 2017 - May. 2019} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Worked as a sole front-end developer in building RPlus, a healthcare web app to generate patient screening reports. (for a client )}
      \item {Designed and developed a PDF generator tool for RPlus using Express \& Puppeteer. More than 10000 reports were published within 3 months of V1 release.}
      \item {Was part of a team that developed an easy-to-use Reimbursement module which connects to home built HR software.}
      \item {Implemented intial ground work for HR pipeline tool.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Front-End Developer} % Job title
  {AdMavin (mavinlabs)} % Organization
  {Bangalore, Karnataka} % Location
  {Oct. 2016 - Dec. 2017} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Was part of a team that developed mavinlabs, a media planning tool which helps customers to zero-in on most optimal outdoor campaign, maximize outreach with minimal budget.}
      \item {Exercised design guidelines to build a responsive user interface for a e-commerce website.}
      \item {Helped out sales team by pitching SaaS platform to potential clients.}
    \end{cvitems}
  }

  %---------------------------------------------------------
\end{cventries}
